\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.15 in,top=0.2in,right=0.15in,bottom=0.1in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sabyasachi Seal} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{
(+91) 891-042-7807 \\ 
Kolkata, India} 

\address{
{}{} \\
\href{mailto:iam.sabyasachi.seal.com}{iam.sabyasachi.seal@gmail.com} \\ \href{https://www.linkedin.com/in/sabyasachi-seal-4461711bb/}{LinkedIn} \\
\href{https://github.com/Sabyasachi-Seal}{GitHub} \\
\href{https://www.codechef.com/users/sabyasachiseal}{CodeChef} \\
\href{www.sabyasachi-seal.github.io}{Portfolio} \\
\href{https://leetcode.com/sabyasachiseal/}{LeetCode} \\
\href{https://medium.com/@yoboy907}{Medium} \\
}

\begin{document}

\begin{rSection}{Education}

{\bf Bachelor of Technology (Computer Science)}: Techno Main Salt Lake \hfill {2020 - 2024}\\
CGPA : 9.30 out of 10.00 (Upto 5th Semester). 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }
Technical Skills: & Cloud Computing(Multi Cloud), Python,  Java, Bash, Linux, GitHub, CI/CD, Jenkins, Jira, MERN Stack.
\\
Soft Skills: & Teamwork, Management, Communication, Creative Thinking, Leadership\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Python Developer Intern} \hfill Nov 2022 - Apr 2022\\
Webknot Technologies \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -2pt {} 
     \item Integrated the Crew Daily Reports into the Unit Reporter Framework
    \item Responsible for fixing the directory structure in the Fileshare for the company.
 \end{itemize}

\textbf{Data Science Intern} \hfill Mar 2022 - Apr 2022\\
The Sparks Foundation \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -2pt {} 
    \item Visualized stock price trends, along with Numerical and Textual Analysis of news for over 5 years. 
    \item Achieved overall 82\% accuracy for stock price predictions using 6 different types of ML Models.
 \end{itemize}
 
\textbf{Microsoft Azure Intern} \hfill Oct 2021 - Jan 2022\\
NASSCOM (FutureSkills Prime) \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -2pt {} 
     \item Deployed a Web Application that Predicted Diabetes(92\% Accurate) using Python, Flask and Azure.
     \item Completed over 60 hours of course work in AZ-104,AZ-204, AZ-500, AI-102, PL-300.
 \end{itemize}

\textbf{ML/AI Intern} \hfill Aug 2021 - Oct 2021\\
Elite Techno Groups \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -2pt {} 
     \item Engineered an Inventory Management System that managed and recorded over 1000 sales for 15+ items using Python.
     \item Spearheaded a team of 4 people for developing models for Cancer Prediction which attained an accuracy of 98\%.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{Cheap-A-Thon (Amazon Price Alert Bot):} {Developed and deployed a bot that tracked the price of products on Amazon which reported up-to 73\% drop in prices using URLLib, Requests, and BeautifulSoup4.}
\href{https://github.com/Sabyasachi-Seal/AmazonPriceDropAlert}{[GitHub]}

\item \textbf{Diabetico (Diabetes Predicting Web App):} {Designed an web app that predicted if a person was diabetic with over 90\% accuracy. Programmed using Python, Flask, SciPy, SKLearn, Pandas, Seaborn}
\href{https://github.com/Sabyasachi-Seal/DiabetesPredictor}{[GitHub]}

\item \textbf{Qwiklabs Progress Tracker:} {Engineered an web app that tracks the progress of participants in Google Cloud Labs. Can be reconfigured for any challenge or pathway. Made using Node, Express, Cheerio, Axios, Pug and GCP for hosting.} \href{https://github.com/Sabyasachi-Seal/QwiklabsProgressTracker}{[GitHub]}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \itemsep -1pt {} 
    \item 	Lead the DevOps team of GDSC TMSL and awarded Gold Milestone as an MLSA \href{https://gdsc.community.dev/techno-main-salt-lake-kolkata/}{[Developer Profile]}
    \item 	Passed Microsoft's AZ-900, AI-900, DP-900, SC-900 and Google's Cloud Digital Leader Exam \href{https://docs.microsoft.com/en-us/users/sabyasachiseal-9602/certifications}{[Certification Profile]}
    \item	Facilitated over 70 students as the to complete GCP Pathways.
    \href{https://cloudskillsboostprogresstracker-j44zd2vilq-uc.a.run.app/}{[GCP Project Link]}
    \item	Solved more than 450 problems on LeetCode and secured 5-stars on HackerRank
    \href{https://leetcode.com/sabyasachiseal/}{[LeetCode]}
    \href{https://www.hackerrank.com/yoboy907}{[HackerRank]}
    \item	Attained over 40 quest and 15 skill Badges on Google Cloud Platform.
    \href{https://www.cloudskillsboost.google/public_profiles/e3e3af1f-e2c8-48b5-ae19-175dee7b6ef5}{[Google Cloud Profile]}
    \item	Selected as a AWS Community Builder under DevTools to publish blogs and tutorials.
    \href{https://www.cloudskillsboost.google/public_profiles/e3e3af1f-e2c8-48b5-ae19-175dee7b6ef5}{[Medium]}
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------




\end{document}
